---
title: "STAT/MATH 495: Problem Set 01"
author: "Brendan Seto"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: hide
    collapsed: false
    smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=8, fig.height=4.5)

# Load packages
library(mosaic)
library(tidyverse)
library(pander)
```

```{r, include=FALSE}
train <- read_csv("https://rudeboybert.github.io/STAT495/static/Titanic/train.csv")
test <- read_csv("https://rudeboybert.github.io/STAT495/static/Titanic/test.csv")
submission <- read_csv("https://rudeboybert.github.io/STAT495/static/Titanic/gender_submission.csv")
```

# Intro

*Goals:* Learn how to sumbit!

*Secondary:* Make a simple model

## Primary Aim

Nothing that I actually have to do here

## Secondary Aim

### Make Models

##### First look at variable names
```{r}
pander(names(train))
```

##### Model with all

First I ran a logistic regresison model with all the non-unique variables.  Here's a summary.  

```{r}
m1 <- glm(Survived~.-PassengerId-Name-Ticket-Cabin, data=train, family = "binomial")

pander(m1)
```

##### Trim 1

I then took only those variables that were significant in the everything model and ran another one.

```{r}
m2 <- glm(Survived~Sex+Pclass+Age, data=train, family = "binomial")

pander(m2)
```


Then I tested it's accuracy.  No matter what the results are, this is the model I'm using.  

```{r}
train1 <- filter(train, !is.na(Age), !is.na(Sex), !is.na(Pclass))

fitted.results <- predict(m2,newdata=subset(train1,select=c("Sex","Pclass","Age")),type='response')
fitted.results <- ifelse(fitted.results > 0.5,1,0)

misClasificError <- mean(fitted.results != train1$Survived)
print(paste('Accuracy',1-misClasificError))
```

Not bad I guess.  Only works if passenger has Age, Sex and Passenger class though.  Will only replace those submissions that have all the variables.  

### Submission

```{r}
predict <- mutate(test, Survived = ifelse(predict(m2,newdata=subset(test,select=c("Sex","Pclass","Age")),type='response')>0.5,1,0))%>%select(PassengerId, Survived)%>%filter(!is.na(Survived))

submission <- anti_join(submission, predict, by = "PassengerId")
submission <- rbind(predict, submission)

write_csv(submission, "submissionBS.csv")
```

We'll see how it works.  Much more i could have done, but good enough warm-up for semester.  